Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-08-08 Paper/app.tex
..

Secondly, we verify the accuracy of the surrogate in a probabilistic setting. In particular, we compare a histogram
plot of the model evaluations (in the cross-validation set) with a PDF evaluated on the same set of samples
using the surrogate, $\tilde{G}$ in Figure~\ref{fig:pdf_33D}. The PDF is evaluated using surrogates constructed for
a 1-dimensional as well as a 2-dimensional active subspace. 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_id_1e4}
\caption{A comparison of the histogram plot based on model evaluations and the PDF based on surrogate
predictions for ignition delay. The two plots are based on samples in the validation set.}
\label{fig:pdf_33D}
\end{center}
\end{figure}
%
In the above comparison, it is observed that the two PDFs are almost identical, thereby confirming a 1-dimensional
active subspace. The modal estimate from either PDF is found to be in agreement with that
based on the histogram plot. Moreover, the spread in the ignition
delay is reasonably captured by the PDFs.

Based on these observations, it can be said that a 1-dimensional surrogate can be used to reasonably approximate the
uncertainty in the ignition delay due to uncertain rate-controlling parameters used in the H$_2$/O$_2$ reaction
mechanism.

>>>>

Secondly, we verify the accuracy of the surrogate in a probabilistic setting. In particular, we compare a histogram
plot of the model evaluations (in the cross-validation set) with a PDF evaluated on the same set of samples
using the surrogate, $\tilde{G}$ in Figure~\ref{fig:pdf_33D}. The PDF is evaluated using surrogates constructed for
a 1-dimensional as well as a 2-dimensional active subspace. 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_id_1e4}
\caption{A comparison of the histogram plot based on model evaluations and the PDF based on surrogate
predictions for ignition delay. The two plots are based on samples in the validation set.}
\label{fig:pdf_33D}
\end{center}
\end{figure}
%
In the above comparison, it is observed that the two PDFs are almost identical, thereby confirming a 1-dimensional
active subspace. The modal estimate from either PDF is observed to be in agreement with that
based on the histogram plot. The mean value based on the set of model evaluations used for verification as well
as the 1-dimensional surrogate was found to be 0.133, whereas, the standard deviations were found to be 0.0198 and 0.0160
respectively. Hence, while the surrogate yields an accurate estimation of the mean, the standard deviation is
under-estimated. This can be understood from the SSP in Figure~\ref{fig:hd} (right) which shows that the model
evaluations do not exactly lie on the linear 1-dimensional surrogate used to capture them. Therefore, the
1-dimensional surrogate can be used to estimate the mean as well as the modal estimate of the ignition delay in
the presence of uncertainty in the 33 parameter considered in this application. The uncertainty associated with the
ignition delay though reasonably close to the true value, is under-estimated.

%\subsection{Surrogate-induced risk analysis}
